\documentclass[12]{article}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=.5in]{geometry}
\usepackage[T1]{fontenc}
\titleformat{\section}
{\huge\bfseries\lowercase}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{0em}
{}

\renewcommand{\maketitle}{
\begin{center}
{\Huge\bfseries
\theauthor}

\vspace{.25em}
 
\vspace{.25em}

michael@vanderlyn.info | 703-973-2077 | https://vanderlyn.info
\end{center}
}


\begin{document}
\title{Resume}
\author{Michael Vanderlyn}
\maketitle
\section{Skills}
\subsection{Programming Languages}
Java, Python, C, Git,  HTML, JS, CSS, PHP, Typescript, Appscript,LaTeX
\subsection{API's and Frameworks}
React.js, Redux, Jquery, Google MDL, Material-ui, Bootstrap,Google  Suite API, OpenCV
\subsection{Non-Programming}
Google Suite, Eclipse, Unix, vim, AWS S3, AWS Lambda, AWS CloudWatch, Microsoft Azure, Agile Methodology, Jira, ssh, puTTY, FileZilla, Android Studio, German Language, PTC Creo Parametric, Microsoft Office
\section{Education}
\subsection{George Mason University| Computer Science | GPA: 3.83 | August 2016 - Present}
\subsection{Thomas Jefferson High School | GPA: 3.93 | September 2012 - June 2016}
\section{Professional Experience}
\subsection{Software Engineer Intern at Blue Ridge Dynamics | September 2018 - Present}
Worked on developing several different projects for customers. Worked primarily with Backbone.js, Jquery, Google Maps API, and Grails. 
\subsection{Northrup Grumman Intern Supporting DHS | June 2018 - August 2018}
Worked on PSPD team under the CBP to develop an internal reporting web portal. Implemented Agile methodology to rapidly develop and deploy a react-redux web application. Learned how to use UML diagrams to assist in designing a project. Worked on a group intern project to develop a different react app to speed up new hire onboarding process.
\subsection{Verizon Digital Media Service Intern | June 2017 - April 2018}
Worked on the Strategic Alliance and Channel Management team to streamline their internal website. Used Google API’s to develop an automated weekly update platform for partner information. Worked on a group intern project to implement Amazon Lambda with video package XML validation.
\section{Projects}
\subsection{Nasdew | October 2016 - April 2017}
Used HTML, CSS, JS, JQuery, Google Maps, and MDL API’s to make the frontend for Nasdew, a fully functioning app that allows users to keep track of items going on sale by inputting and viewing prices of items in their area.
\subsection{CampusUnite | September 2015 - June 2016}
Built a fully functioning app utilizing android mobile and web platforms along with a database, and data streaming technology for instant messaging functionality.
\end{document}
